Meta-analytic findings of the self-controlled motor learning literature: Underpowered, biased, and lacking evidential value

### 2021-08-18 docs/revision/manuscript-revised.Rmd
update: add missing reference

keywords          : "Motor learning, retention, choice, ``OPTIMAL'' theory, meta-analysis, p-curve, publication bias"
# wordcount         : "5055"
bibliography      : ["../refs.bib"]
annotate_references: yes
nocite: |
  @Aiken2012-po,@Alami2013-gy,@Ali2012-rq,@Andrieux2016-lf,@Andrieux2012-dj,@Arsal2004-kf,@Barros2010-pc,@Barros2019-my,@Bass2015-cc,@Bass2018-vz,@Brydges2009-zb,@Bund2004-hy,@Carter2012-sj,@Chen2002-vg,@Chiviacowsky2014-ob,@Chiviacowsky2017-fy,@Chiviacowsky2002-ep,@Chiviacowsky2012-pk,@Chiviacowsky2008-bj,@Chiviacowsky2012-ri,@davis2009-dt,@Fagundes2013-ge,@Fairbrother2012-gz,@Ferreira2019-zo,@Figueiredo2018-kw,@Ghorbani2019-yz,@Grand2015-de,@Grand2017-de,@Hansen2011-rr,@Hartman2007-uv,@Hemayattalab2013-mq,@Ho2016-on,@Holmberg2013-qk,@Huet2009-wu,@Ikudome2019-ru,@Jalalvand2019-im,@Janelle1997-ht,@jones2010-qw,@Kaefer2014-bs,@Keetch2007-yp,@Kim2019-sl,@Leiker2016-zd,@Leiker2019-fz,@Lemos2017-qx,@Lessa2015-eq,@Lewthwaite2015-bd,@Lim2015-qs,@Marques2016-aw,@Marques2017-ue,@Norouzi2016-cx,@Nunes2019-nr,@Ostrowski2015-nb,@Patterson2010-tk,@Patterson2010-uu,@Patterson2013-nh,@Patterson2011-vt,@Post2016-vg,@Post2011-qc,@Post2014-yi,@Rydberg2011-zg,@Sanli2013-qh,@Ste-Marie2013-uc,@Tsai2015-rj,@Von_Lindern2017-al,@Williams2017-pj,@Wu2011-ha,@wu2007self,@Wulf2014-sn,@Wulf1999-pn,@Wulf2001-nb,@Wulf2018-ie,@Wulf2005-sz

>>>>

keywords          : "Motor learning, retention, choice, ``OPTIMAL'' theory, meta-analysis, p-curve, publication bias"
# wordcount         : "5055"
bibliography      : ["../refs.bib"]
annotate_references: yes
nocite: |
  @Aiken2012-po,@Alami2013-gy,@Ali2012-rq,@Andrieux2016-lf,@Andrieux2012-dj,@Arsal2004-kf,@Barros2010-pc,@Barros2019-my,@Bass2015-cc,@Bass2018-vz,@Brydges2009-zb,@Bund2004-hy,@Carter2012-sj,@Chen2002-vg,@Chiviacowsky2014-ob,@Chiviacowsky2017-fy,@Chiviacowsky2002-ep,@Chiviacowsky2012-pk,@Chiviacowsky2008-bj,@Chiviacowsky2012-ri,@davis2009-dt,@Fagundes2013-ge,@Fairbrother2012-gz,@Ferreira2019-zo,@Figueiredo2018-kw,@Ghorbani2019-yz,@Grand2015-de,@Grand2017-de,@Hansen2011-rr,@Hartman2007-uv,@Hemayattalab2013-mq,@Ho2016-on,@Holmberg2013-qk,@Huet2009-wu,@Ikudome2019-ru,@Jalalvand2019-im,@Janelle1997-ht,@jones2010-qw,@Kaefer2014-bs,@Keetch2007-yp,@Kim2019-sl,@Leiker2016-zd,@Leiker2019-fz,@Lemos2017-qx,@Lessa2015-eq,@Lewthwaite2015-bd,@Lim2015-qs,@Marques2016-aw,@Marques2017-ue,@Norouzi2016-cx,@Nunes2019-nr,@Ostrowski2015-nb,@Patterson2010-tk,@Patterson2010-uu,@Patterson2013-nh,@Patterson2011-vt,@Post2016-vg,@Post2011-qc,@Post2014-yi,@Rydberg2011-zg,@Sanli2013-qh,@Ste-Marie2013-uc,@Tsai2015-rj,@Von_Lindern2017-al,@Williams2017-pj,@Wu2011-ha,@wu2007self,@Wulf2014-sn,@Wulf1999-pn,@Wulf2001-nb,@Wulf2018-ie,@Wulf2005-sz,@wulf2015-mg
